Blog post: Different map projections

### 2020-03-17 text/20/map-projections.Rmd
More Colorado maps

```{r mercator}
projection_string <- "+proj=tmrec +lon_0=-80 +lat_0=0 +ellps=WGS84 +no_defs"
projection_string <- "+proj=merc +lon_0=0 +k=1 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
countries %>%
  ggplot() + 
  geom_sf(fill="white") + 
  geom_sf(data=co, color="red", fill="white") +
  coord_sf(crs=projection_string, ylim=c(-80,80))
```

>>>>

```{r mercator}
projection_string <- "+proj=merc +lon_0=0 +k=1 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
projection_string <- "+proj=merc +lon_0=0 +k=1 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +no_defs"
co %>%
  ggplot() + 
  geom_sf(color="red", fill="white") +
  coord_sf(crs=projection_string)
```

```{r laea}
projection_string <- "+proj=merc +lon_0=0 +k=1 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
projection_string <- "+proj=laea +lon_0=-105.5 +lat_0=39 +ellps=WGS84 +datum=WGS84 +no_defs"
co %>%
  ggplot() + 
  geom_sf(color="red", fill="white") +
  coord_sf(crs=projection_string)
```
